\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-30 OaklandSubmission/intro.tex
till correctness
nits

\subsubsection*{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem relates the
``trusted third party'' semantics of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The theorem
guarantees that for a well-typed source program, the two semantics
successfully terminate
(e.g. there are no array index out-of-bounds errors), and that the
observable outputs in the two semantics are
identical. For
the security theorem, we formally reduce the security
of our compiler to the security of the  \mpc back-end
 (by also invoking our correctness theorem). We also prove a formal security theorem for our partitioning
scheme.

\subsubsection*{Evaluation} We have implemented the \tool toolchain
using ABY~\cite{aby} as the
cryptographic back-end. We evaluate \tool by implementing a wide range
of secure prediction benchmarks including linear and na\"{i}ve bayes
classifiers, decision trees, deep neural networks, state-of-the-art
classifiers from Tensorflow~\cite{tensorflow}
and \bonsai~\cite{bonsai}, and also the matrix factorization example
from Nikolaenko et al.~\cite{valeriaMatrix}. Our results demonstrate
three key points. First, \tool makes it convenient for general
programmers to write \mpc protocols. E.g. we provide the first \mpc
implementation of \bonsai~\cite{bonsai}, and it was programmed in the
high-level \tool source language by a non-cryptographer. Second, the
performance
of the protocols
generated by \tool are comparable to or better than (up to 19x in some
cases) their state-of-the-art specialized implementations. Finally, we
show that with partitioning, we are able to implement applications
that require more than 300 million gates.

@@

The rest of the paper is structured as follows. We formalize \tool and
prove its correctness and security theorems in
Section~\ref{sec:ld}. Section~\ref{sec:pipe} details our partitioning
scheme and proves its security. Section~\ref{sec:impl}
presents the implementation details, and
Section~\ref{sec:eval} present a comprehensive evaluation of \tool. We
begin with an overview of \tool through an example in
Section~\ref{sec:ex}. %\nc{provided a pointer to sec 2 as well.}
%\aseem{Sure :), I did not add it because Sec. 2 was just next line, so
%  I thought it did not need a pointer.}

>>>>

\subsubsection*{Formal guarantees} We prove formal correctness and
security theorems for our compiler. The correctness theorem relates the
``trusted third party'' semantics of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The theorem
guarantees that for a well-typed source program, the two semantics
successfully terminate
(e.g. there are no array index out-of-bounds errors), with identical
observable outputs. For
the security theorem, we formally reduce the security
of our compiler to the security of the  \mpc back-end
 (by also invoking our correctness theorem). We also prove a formal security theorem against semi-honest (or, ``honest but curious") adversaries for our partitioning
scheme (Section~\ref{sec:ld} and Section~\ref{sec:pipe}).

\subsubsection*{Evaluation} We have implemented \tool
using ABY~\cite{aby} as the
cryptographic back-end. We evaluate \tool by implementing a wide range
of secure prediction benchmarks including linear and na\"{i}ve bayes
classifiers, decision trees, deep neural networks, state-of-the-art
classifiers from Tensorflow~\cite{tensorflow}
and \bonsai~\cite{bonsai}, and also the matrix factorization example
from Nikolaenko et al.~\cite{valeriaMatrix}. Our results demonstrate
three key points. First, \tool makes it convenient for general
programmers to write \mpc protocols. E.g. we provide the first \mpc
implementation of \bonsai~\cite{bonsai}, and it was programmed in the
high-level \tool source language by a non-cryptographer. Second, the
performance
of the protocols
generated by \tool are comparable to or better than (up to 19x in some
cases) their state-of-the-art specialized implementations. Finally, we
show that partitioning enables us to implement applications
that require more than 300 million gates (Section~\ref{sec:impl} and
Section~\ref{sec:eval}).

@@

%% The rest of the paper is structured as follows. We formalize \tool and
%% prove its correctness and security theorems in
%% Section~\ref{sec:ld}. Section~\ref{sec:pipe} details our partitioning
%% scheme and proves its security. Section~\ref{sec:impl}
%% presents the implementation details, and
%% Section~\ref{sec:eval} present a comprehensive evaluation of \tool. We
%% begin with an overview of \tool through an example in
%% Section~\ref{sec:ex}. %\nc{provided a pointer to sec 2 as well.}
%\aseem{Sure :), I did not add it because Sec. 2 was just next line, so
%  I thought it did not need a pointer.}
